ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-07 paper/paper.tex
update

 \item Both 2-folds and 10-folds stacking gives improvement on AUC, but 10-folds stacking shows
  discrepancy in improvement between Cross Validation and 30\% of testing data.
\end{enumerate}

@@

\textbf{Fig. 1} shows the AUC performance of 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 AUC is improved once stacking is applied and we included more randomized stacking features until there is no improvement in AUC.

\begin{figure}[ht!]
\centering
\includegraphics[width=110mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

>>>>

 \item Both 2-folds and 10-folds stacking gives improvement on $AUC$, but 10-folds stacking shows
  discrepancy in improvement between Cross Validation and 30\% of testing data.
\end{enumerate}

@@

\textbf{Fig. 1} shows the $AUC$ of 5-folds Cross Validation using same parameters and seed and $AUC$ of prediction on 30\% of testing data .
 There is a strong correlation in $AUC$ between Cross Validation and 30\% of testing data.
 $AUC$ is improved once stacking is applied and we included more randomized stacking features until there is no improvement.

\begin{figure}[ht!]
\centering
\includegraphics[width=100mm]{Rplot.png}
\caption{$AUC$ of 5-folds CV result and 30\% testing data using different number of stacking features. The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}
